Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
slightly shorter intro

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  As social coding sites attract
more users and projects become more popular, they receive ever more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions. 
%
Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
These methods can become a bottleneck, and thus it is beneficial to prioritize certain
contributions.  This prioritization can be achieved with predictors of a
contribution's quality.

The decision to include code in
a project has been described as a meritocracy, where only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of continuous integration.  While pull requests
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors involved in continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

In particular, we analyzed contributions in the 
context of continuous integration, using technical factors and one social
factor from the challenge
corpus~\cite{msr17challenge}, and social factors from a developer's
GitHub profile.  We used the technical factors to estimate the commit's
complexity, and the social factors to estimate the developer's experience.
Overall, our study investigates how different technical and social factors predict
contribution quality. This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

We find that social factors are an important aspect of build success but
these factors alone do not fully predict whether a contribution will be successfully 
pass the build tests. We find
that core team members are more likely to achieve build success than non-core
members, and that developers with more followers are more likely to submit commits that pass the
continuous integration build.

>>>>

\section{Introduction}
For managers of an open source project, it is important to ensure that the
project consists of high quality contributions.  As social coding sites attract
more users and projects become more popular, they receive ever more
community contributions.  As the number of contributions to a project increase,
the project must dedicate more time to vetting these contributions. 
%
Over the years, the open source
community has developed various techniques to vet project contributions, such as pull
requests which must be approved by a core team member~\cite{gousios14}. 
This can become a bottleneck, and thus it is beneficial to prioritize certain
contributions, ideally by predicted quality.

Ideally, the decision to include code in
a project is meritocratic, such that only the code is a factor
in the decision~\cite{Scacchi07}.
While one would think that only the complexity of the commit is important, past
studies have shown that the developer making the commit is also an important
indicator when investigating contribution quality~\cite{tsay14icse, tsay14fse}.
Thus, both technical factors, which describe the complexity of the commit, and
social factors, which describe the developer's experience, are important when
investigating contribution quality.

This previous work has focused on the predicted acceptance of \emph{pull requests}. 
By contrast,  we are interested in analyzing the quality 
of a contribution in the context of \emph{continuous integration}.  While pull request
quality is determined through manual inspection, continuous integration quality
is automatically determined through test cases, and thus approach the problem of
quality determination differently.
We investigate the factors related to continuous integration build success.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

We analyzed contributions in the 
context of continuous integration using technical factors and one social
factor from the challenge
corpus~\cite{msr17challenge}, and social factors from a developer's
GitHub profile.  We used the technical factors to estimate the commit's
complexity, and the social factors to estimate the developer's experience.
Overall, our study investigates how different technical and social factors predict
contribution quality. This information can help core team members prioritize project
contributions, and increases understanding of quality enforcement
in software development.

We find that social factors are an important aspect of build success ,
do not fully predict whether a contribution will 
pass all build tests;
that core team members are more likely to achieve build success than non-core
members; and that developers with more followers are more likely to submit commits that pass the
continuous integration build.
